SSwAB-IT Phase 1 Analysis

### 2025-11-24 Jordana Hoppe/SSwAB-IT/phase_1_analysis.qmd
nicer SSwAB-IT tables

```{r setup}
#| include: false
library(keyring)
library(redcapAPI)
library(tidyverse)
library(gt)
library(gtsummary)
library(caret)
library(epiR)
library(eulerr)
library(ggpubr)
home_dir <- switch(Sys.info()["sysname"],
    "Darwin" = "/Users/tim/Library/CloudStorage/OneDrive-TheUniversityofColoradoDenver/Vigers/CF/Jordana Hoppe/SSwAB-IT",
    "Linux" = "/home/timvigers/OneDrive/Vigers/CF/Jordana Hoppe/SSwAB-IT"
)
knitr::opts_knit$set(root.dir = home_dir)
```

@@

```{r}
agreement <- function(bug, data = df) {
    cos <- paste0(bug, "_cos")
    sos <- paste0(bug, "_sos")
    d <- data[, c(cos, sos)]
    colnames(d) <- c("COS", "SOS")
    d <- d[complete.cases(d), ]
    # Agreement metrics
    c <- confusionMatrix(
        d$SOS,
        reference = d$COS,
        positive = "Positive",
        mode = "everything",
        dnn = c("SOS", "COS")
    )
    pabak <- epi.kappa(table(d$COS, d$SOS))
    # Print
    cat("\n")
    cat("\n")
    cat("####", "2x2 Table")
    cat("\n")
    cat("\n")
    d %>%
        tbl_cross(percent = "cell") %>%
        print()
    cat("\n")
    cat("\n")
    cat("####", "2x2 Table (With CIs)")
    cat("\n")
    cat("\n")
    d %>%
        tbl_summary(by = COS, percent = "cell") %>%
        add_ci(method = list(all_categorical() ~ "wald")) %>%
        print()
    cat("\n")
    cat("\n")
    cat(
        "Overall accuracy (both negative/negative and positive/positive) was ",
        scales::percent(c$overall["Accuracy"], accuracy = 0.1),
        " (95% CI: ",
        scales::percent(c$overall["AccuracyLower"], accuracy = 0.1),
        " - ",
        scales::percent(c$overall["AccuracyUpper"], accuracy = 0.1),
        ").",
        sep = ""
    )
    cat("\n")
    cat("\n")
    cat(
        "Kappa was ",
        round(pabak$kappa$est, 3),
        " (95% CI: ",
        round(pabak$kappa$lower, 3),
        " - ",
        round(pabak$kappa$upper, 3),
        ")",
        ".",
        sep = ""
    )
    cat("\n")
    cat("\n")
    cat(
        "Prevalence and Bias Adjusted Kappa (PABAK) was ",
        round(pabak$pabak$est, 3),
        " (95% CI: ",
        round(pabak$pabak$lower, 3),
        " - ",
        round(pabak$pabak$upper, 3),
        ")",
        ".",
        sep = ""
    )
    cat("\n")
    cat("\n")
    cat("#### Euler diagram of negative results")
    cat("\n")
    cat("\n")
    print(plot(euler(d == "Negative"), quantities = list(cex = 3)))
    cat("\n")
    cat("\n")
    cat("#### Euler diagram of positive results")
    cat("\n")
    cat("\n")
    print(plot(euler(d == "Positive"), quantities = list(cex = 3)))
    cat("\n")
    cat("\n")
}
agreement_test <- function(bug, group = "group", data = df) {
    # Prepare data
    cos <- paste0(bug, "_cos")
    sos <- paste0(bug, "_sos")
    d <- data[, c(cos, sos, group)]
    d <- d[complete.cases(d), ]
    colnames(d) <- c("COS", "SOS", "Group")
    # Agreement and detailed agreement
    d$agree <- d$COS == d$SOS
    d$detailed_agree <- paste0("COS ", d$COS, "/", "SOS ", d$SOS)
    d$detailed_agree <- factor(
        d$detailed_agree,
        levels = c(
            "COS Negative/SOS Negative",
            "COS Negative/SOS Positive",
            "COS Positive/SOS Negative",
            "COS Positive/SOS Positive"
        ),
        labels = c("COS-/SOS-", "COS-/SOS+", "COS+/SOS-", "COS+/SOS+")
    )
    # Print
    cat("\n")
    cat("\n")
    d %>%
        select(agree, detailed_agree, Group) %>%
        tbl_summary(
            by = Group,
            missing_text = "Missing",
            label = list(
                agree ~ "Agree (+/+ and -/-)",
                detailed_agree ~ "Detailed Agreement"
            )
        ) %>%
        add_overall() %>%
        add_p(test.args = all_tests("fisher.test") ~ list(workspace = 2e9)) %>%
        separate_p_footnotes() %>%
        modify_footnote(everything() ~ NA) %>%
        print()
    cat("\n")
    cat("\n")
}
```

>>>>

```{r setup}
#| include: false
library(keyring)
library(redcapAPI)
library(gt)
library(gtsummary)
library(caret)
library(epiR)
library(eulerr)
library(ggpubr)
library(tidyverse)
home_dir <- switch(
  Sys.info()["sysname"],
  "Darwin" = "/Users/tim/Library/CloudStorage/OneDrive-TheUniversityofColoradoDenver/Vigers/CF/Jordana Hoppe/SSwAB-IT",
  "Linux" = "/home/timvigers/OneDrive/Vigers/CF/Jordana Hoppe/SSwAB-IT"
)
knitr::opts_knit$set(root.dir = home_dir)
```

@@

```{r}
agreement <- function(bug, data = df) {
  cos <- paste0(bug, "_cos")
  sos <- paste0(bug, "_sos")
  d <- data[, c(cos, sos)]
  colnames(d) <- c("COS", "SOS")
  d <- d[complete.cases(d), ]
  # Agreement metrics
  c <- confusionMatrix(
    d$SOS,
    reference = d$COS,
    positive = "Positive",
    mode = "everything",
    dnn = c("SOS", "COS")
  )
  pabak <- epi.kappa(table(d$COS, d$SOS))
  # Print
  cat("\n")
  cat("\n")
  cat("####", "2x2 Table")
  cat("\n")
  cat("\n")
  d1 = d %>%
    tbl_cross(percent = "cell", digits = c(0, 1)) %>%
    print()
  cat("\n")
  cat("\n")
  cat("####", "2x2 Table (With CIs)")
  cat("\n")
  cat("\n")
  d %>%
    tbl_summary(
      by = COS,
      percent = "cell",
      digits = list("SOS" ~ c(0, 1))
    ) %>%
    add_ci(
      pattern = "{stat} [{ci}]",
      method = list(all_categorical() ~ "wald"),
      style_fun = all_categorical() ~ label_style_number(
        scale = 100,
        digits = 1
      )
    ) %>%
    print()
  cat("\n")
  cat("\n")
  cat(
    "Overall accuracy (both negative/negative and positive/positive) was ",
    scales::percent(c$overall["Accuracy"], accuracy = 0.1),
    " (95% CI: ",
    scales::percent(c$overall["AccuracyLower"], accuracy = 0.1),
    " - ",
    scales::percent(c$overall["AccuracyUpper"], accuracy = 0.1),
    ").",
    sep = ""
  )
  cat("\n")
  cat("\n")
  cat(
    "Kappa was ",
    round(pabak$kappa$est, 3),
    " (95% CI: ",
    round(pabak$kappa$lower, 3),
    " - ",
    round(pabak$kappa$upper, 3),
    ")",
    ".",
    sep = ""
  )
  cat("\n")
  cat("\n")
  cat(
    "Prevalence and Bias Adjusted Kappa (PABAK) was ",
    round(pabak$pabak$est, 3),
    " (95% CI: ",
    round(pabak$pabak$lower, 3),
    " - ",
    round(pabak$pabak$upper, 3),
    ")",
    ".",
    sep = ""
  )
  cat("\n")
  cat("\n")
  cat("#### Euler diagram of negative results")
  cat("\n")
  cat("\n")
  print(plot(euler(d == "Negative"), quantities = list(cex = 3)))
  cat("\n")
  cat("\n")
  cat("#### Euler diagram of positive results")
  cat("\n")
  cat("\n")
  print(plot(euler(d == "Positive"), quantities = list(cex = 3)))
  cat("\n")
  cat("\n")
}
agreement_test <- function(bug, group = "group", data = df) {
  # Prepare data
  cos <- paste0(bug, "_cos")
  sos <- paste0(bug, "_sos")
  d <- data[, c(cos, sos, group)]
  d <- d[complete.cases(d), ]
  colnames(d) <- c("COS", "SOS", "Group")
  # Agreement and detailed agreement
  d$agree <- d$COS == d$SOS
  d$detailed_agree <- paste0("COS ", d$COS, "/", "SOS ", d$SOS)
  d$detailed_agree <- factor(
    d$detailed_agree,
    levels = c(
      "COS Negative/SOS Negative",
      "COS Negative/SOS Positive",
      "COS Positive/SOS Negative",
      "COS Positive/SOS Positive"
    ),
    labels = c("COS-/SOS-", "COS-/SOS+", "COS+/SOS-", "COS+/SOS+")
  )
  # Print
  cat("\n")
  cat("\n")
  d %>%
    select(agree, detailed_agree, Group) %>%
    tbl_summary(
      by = Group,
      missing_text = "Missing",
      label = list(
        agree ~ "Agree (+/+ and -/-)",
        detailed_agree ~ "Detailed Agreement"
      ),
      digits = list(c("agree", "detailed_agree") ~ c(0, 1))
    ) %>%
    add_overall() %>%
    add_p(
      test = list(agree ~ "chisq.test", detailed_agree ~ "fisher.test"),
      test.args = all_tests("fisher.test") ~ list(workspace = 2e9)
    ) %>%
    separate_p_footnotes() %>%
    modify_footnote(everything() ~ NA) %>%
    print()
  cat("\n")
  cat("\n")
}
```
